Supplementary material

### 2022-04-13 submission/supplement.rmd
fix y-axis in shiny plots + add directory descriptions to readme + update formulas in supplement

\begin{equation}
P(Y=1\given X=x,Z=z) = g(x^t\beta + \gamma z)
\end{equation}
(\#eq:risk)

@@

where $f(\hat{lp}, z) = \hat{lp}+\hat{\gamma}z$, with $\hat{\gamma}$ the
estimated relative treatment effect (log odds ratio).

@@

$$ f(\hat{lp}, z) = \gamma_0+\gamma_1z+\gamma_2\hat{lp}+\gamma_3z\hat{lp} $$

@@

$$ f(\hat{lp}, z) = \gamma_0 + \gamma_1z+zs(\hat{lp}) $$
where
$$s(x)=\alpha_0+\alpha_1h_1(x)+\alpha_2h_2(x)+\dots+\alpha_{k-1}h_{k-1}(x)$$
with $h_1(x)=x$ and for $j=2,\dots,k-2$
$$h_{j+1}(x)= (x-t_j)^3-(x-t_{k-1})_+^3 \frac{t_k-t_j}{t_k-t_{k-1}}+(x-t_k)^3_+\frac{t_{k-1}-t_j}{t_k-t_{k-1}}$$
where 
$t_1,\dots,t_k$ are the selected knots [@harrell2017regression].

>>>>

\begin{equation}
P(Y=1\given X=x,Z=z) = g(x^t\beta + \delta_0 z)
\end{equation}
(\#eq:risk)

@@

where $f(\hat{lp}, z) = \hat{lp}+\hat{\delta}_0z$, with $\hat{\delta}_0$ the
estimated relative treatment effect (log odds ratio).

@@

$$ f(\hat{lp}, z) = \delta_0+\delta_1z+\delta_2\hat{lp}+\delta_3z\hat{lp} $$

@@

$$ f(\hat{lp}, z) = \delta_0 + \delta_1z+zs(\hat{lp}) $$
where
$$s(x)=\alpha_0+\alpha_1h_1(x)+\alpha_2h_2(x)+\dots+\alpha_{k-1}h_{k-1}(x)$$
with $h_1(x)=x$ and for $j=2,\dots,k-2$
$$h_{j+1}(x)= (x-t_j)^3-(x-t_{k-1})_+^3 \frac{t_k-t_j}{t_k-t_{k-1}}+(x-t_k)^3_+\frac{t_{k-1}-t_j}{t_k-t_{k-1}}$$
where 
$t_1,\dots,t_k$ are the selected knots [@harrell2017regression].
